ICML submission

### 2020-08-03 shinymice/www/about.Rmd
Fix light/dark themes
Show dataset name instead of variables in Impute tab

This Shiny app has the sole purpose of showing that I'm able to program an app in `R Shiny`. However, if all goes well, I might use this as the foundation of the interactive evaluation suite for evaluating multiply imputed data that I'm developing as Research Master's thesis project. 'ShinyMICE' will be integrated into the `mice()` environment in `R`.

Watch the current state of the project on [github.com/gerkovink/ShinyMICE](https://github.com/gerkovink/ShinyMICE/).

>>>>

This Shiny app has the sole purpose of showing that I'm able to program an app in `R Shiny`. However, if all goes well, I might use this as the foundation of the interactive evaluation suite for evaluating multiply imputed data that I'm developing as Research Master's thesis project. `shinymice` will be integrated into the `mice` environment in `R`.

Watch the current state of the project on [github.com/gerkovink/shinyMice](https://github.com/gerkovink/shinyMice/).
